Comparing distance distributions for top predictive features between bins with and without TADs

### 2019-04-19 Scripts/comparing_distance_densities_by_genomic_bin_class.Rmd
editted results script

## Function for ploting distance densities between bins with and without TAD boundaries

```{r}
distplotsfunc <- function(cl, resolution, annotation){
  train <- readRDS(paste0("Z:/TAD_data_analysis/", cl, "/", resolution, "/training_testing/train.rds"))
  data <- train[, c(1, which(names(train)==annotation))]

  set.seed(123)
  majorityids <- sample(x=which(data$y=="No"), size=length(which(data$y=="Yes")))
  annotdata <- rbind.data.frame(data[which(data$y=="Yes"),],
                                data[majorityids,])

  #ks.test(annotdata[which(annotdata$y=="No"),2], annotdata[which(annotdata$y=="Yes"),2], alternative = "two.sided")

  perm.pval <- pvalue(oneway_test(annotdata[,2] ~ annotdata[,1],
                     data=annotdata,
                     alternative="greater", 
                     distribution=approximate(B=10000)))[1]

  if(perm.pval==0){perm.pval="< 0.0001"}

  plottitle <- paste(gsub(paste(c("Gm12878",
                                  "-","_",
                                  "dist","perc","count",
                                  "Haib",
                                  "Sydh",
                                  "Uta",
                                  "Uw",
                                  "Broad",
                                  "Uchicago"), 
                                collapse = "|"), 
                          "",
                          annotation))

  p <- ggplot(annotdata, aes(x=annotdata[,2], color=y)) +
    geom_density() +
    scale_color_discrete(name="Class of\nGenomic Bin",
                         labels=c("Does not overlap\nw/ flanked TAD boundary", "Overlapped w/\nflanked TAD boundary")) +
    ylab("Frequency") +
    xlab("Log2 Distance") +
    ggtitle(paste(plottitle)) +
    annotate("text", x=7, y=.2, label= paste("P-Value:", perm.pval, sep = " "), size=5) +
    theme_bw() +
    theme(axis.text.x = element_text(size=15 #,
                                      #angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      #hjust = 1
     ),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20,
                               hjust=.5))

  ggsave(p, 
         filename = paste0("C:/Users/stili/Documents/TAD_miscellaneous/figures/comparing_distance_by_bin_class/", 
                           cl, 
                           "_", 
                           resolution, 
                           "_", 
                           plottitle, 
                           ".png"),
         width=10,
         height=10,
         units="in")
}

@@

### 10kb

#### Top Annotations

```{r}
#### CTCF

distplotsfunc(cl="GM12878", resolution="10kb", annotation="Gm12878-Ctcf-Broad_dist")

#### Smc3ab9263

distplotsfunc(cl="GM12878", resolution="10kb", annotation="Gm12878-Smc3ab9263-Sydh_dist")

#### Znf143166181ap

distplotsfunc(cl="GM12878", resolution="10kb", annotation="Gm12878-Znf143166181ap-Sydh_dist")

#### Rad21

distplotsfunc(cl="GM12878", resolution="10kb", annotation="Gm12878-Rad21-Haib_dist")

#### 08Insulator

distplotsfunc(cl="GM12878", resolution="10kb", annotation="Gm12878-08Insulator_dist")

#### Yy1sc281

distplotsfunc(cl="GM12878", resolution="10kb", annotation="Gm12878-Yy1sc281-Haib_dist")

#### DNase

distplotsfunc(cl="GM12878", resolution="10kb", annotation="Gm12878-DNase_dist")
```

### 25kb

#### Top Annotations

```{r}
#### CTCF

distplotsfunc(cl="GM12878", resolution="25kb", annotation="Gm12878-Ctcf-Broad_dist")

#### Smc3ab9263

distplotsfunc(cl="GM12878", resolution="25kb", annotation="Gm12878-Smc3ab9263-Sydh_dist")

#### Znf143166181ap

distplotsfunc(cl="GM12878", resolution="25kb", annotation="Gm12878-Znf143166181ap-Sydh_dist")

#### Rad21

distplotsfunc(cl="GM12878", resolution="25kb", annotation="Gm12878-Rad21-Haib_dist")

#### 08Insulator

distplotsfunc(cl="GM12878", resolution="25kb", annotation="Gm12878-08Insulator_dist")

#### Yy1sc281

distplotsfunc(cl="GM12878", resolution="25kb", annotation="Gm12878-Yy1sc281-Haib_dist")

#### DNase

distplotsfunc(cl="GM12878", resolution="25kb", annotation="Gm12878-DNase_dist")
```

### 50kb

#### Top Annotations

```{r}
#### CTCF

distplotsfunc(cl="GM12878", resolution="50kb", annotation="Gm12878-Ctcf-Broad_dist")

#### Smc3ab9263

distplotsfunc(cl="GM12878", resolution="50kb", annotation="Gm12878-Smc3ab9263-Sydh_dist")

#### Znf143166181ap

distplotsfunc(cl="GM12878", resolution="50kb", annotation="Gm12878-Znf143166181ap-Sydh_dist")

#### Rad21

distplotsfunc(cl="GM12878", resolution="50kb", annotation="Gm12878-Rad21-Haib_dist")

#### 08Insulator

distplotsfunc(cl="GM12878", resolution="50kb", annotation="Gm12878-08Insulator_dist")

#### Yy1sc281

distplotsfunc(cl="GM12878", resolution="50kb", annotation="Gm12878-Yy1sc281-Haib_dist")

#### DNase

distplotsfunc(cl="GM12878", resolution="50kb", annotation="Gm12878-DNase_dist")
```

### 100kb

#### Top Annotations

```{r}
#### CTCF

distplotsfunc(cl="GM12878", resolution="100kb", annotation="Gm12878-Ctcf-Broad_dist")

#### Smc3ab9263

distplotsfunc(cl="GM12878", resolution="100kb", annotation="Gm12878-Smc3ab9263-Sydh_dist")

#### Znf143166181ap

distplotsfunc(cl="GM12878", resolution="100kb", annotation="Gm12878-Znf143166181ap-Sydh_dist")

#### Rad21

distplotsfunc(cl="GM12878", resolution="100kb", annotation="Gm12878-Rad21-Haib_dist")

#### 08Insulator

distplotsfunc(cl="GM12878", resolution="100kb", annotation="Gm12878-08Insulator_dist")

#### Yy1sc281

distplotsfunc(cl="GM12878", resolution="100kb", annotation="Gm12878-Yy1sc281-Haib_dist")

#### DNase

distplotsfunc(cl="GM12878", resolution="100kb", annotation="Gm12878-DNase_dist")
```

>>>>

## 10kb

```{r}
train <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/training_testing/train.rds"))

enetcoefs <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/Distance/ENET/enetcoefs.rds"))

names(train) <- gsub(paste(c("`", 
                             "Gm12878", 
                             "-", 
                             #"_", 
                             #"dist", "count", "perc",
                             "Haib", 
                             "Sydh",
                             "Uta",
                             "Uw",
                             "Broad",
                             "Uchicago"), collapse = "|"), "", names(train))
train <- train[,c(1,which(names(train) %in% enetcoefs))]

set.seed(123)
train_smote <- SMOTE(y ~ ., 
                     data=train, 
                     perc.over = 100, 
                     perc.under = 200)

@@

### Top Annotations

####SMC

```{r}
annotname <- gsub(paste(c("`", 
             "Gm12878", 
             "-", 
             #"_", 
             #"dist", "count", "perc",
             "Haib", 
             "Sydh",
             "Uta",
             "Uw",
             "Broad",
             "Uchicago"), collapse = "|"), "", "Gm12878-Smc3ab9263-Sydh_dist")

annotdata.smc <- train_smote[, c(1, which(names(train_smote)==annotname))]

#ks.test(annotdata.smc[which(annotdata.smc$y=="No"),2], annotdata.smc[which(annotdata.smc$y=="Yes"),2], alternative = "two.sided")

perm.pval <- pvalue(oneway_test(annotdata.smc[,2] ~ annotdata.smc[,1],
                     data=annotdata.smc,
                     alternative="greater", 
                     distribution=approximate(B=10000)))[1]

perm.pval <- ifelse(perm.pval==0,"< 0.0001", as.character(round(perm.pval,4)))

plottitle <- paste(gsub(paste(c("Gm12878",
                                  "-","_",
                                  "dist","perc","count",
                                  "Haib",
                                  "Sydh",
                                  "Uta",
                                  "Uw",
                                  "Broad",
                                  "Uchicago"), 
                                collapse = "|"), 
                          "",
                          "Gm12878-Smc3ab9263-Sydh_dist"))

p.gm12878.10kb.smc <- ggplot(annotdata.smc, aes(x=Smc3ab9263_dist, color=y)) +
    geom_density() +
    scale_color_discrete(name="Class of\nGenomic Bin",
                         labels=c("Does not overlap\nw/ flanked TAD boundary", "Overlapped w/\nflanked TAD boundary")) +
    ylab("") +
    xlab("") +
    ggtitle("SMC3a\nPermutation P-Value: < 0.0001") +
    #annotate("text", x=7, y=.2, label= paste("P-Value:", perm.pval, sep = " "), size=5) +
    theme_bw() +
    theme(axis.text.x = element_text(size=15 #,
                                     #angle = 45, 
                                     #margin = ggplot2::margin(t = 35),
                                     #hjust = 1
    ),
    axis.text.y = element_text(size = 15),
    axis.title.x = element_text(size = 20),
    axis.title.y = element_text(size = 20),
    legend.text=element_text(size=15),
    legend.title=element_text(size=20),
    plot.title = element_text(size=20,
                              hjust=.5))
```

####ZNF143

```{r}
annotname <- gsub(paste(c("`", 
             "Gm12878", 
             "-", 
             #"_", 
             #"dist", "count", "perc",
             "Haib", 
             "Sydh",
             "Uta",
             "Uw",
             "Broad",
             "Uchicago"), collapse = "|"), "", "Gm12878-Znf143166181ap-Sydh_dist")

annotdata.znf143 <- train_smote[, c(1, which(names(train_smote)==annotname))]

#ks.test(annotdata.znf143[which(annotdata.znf143$y=="No"),2], annotdata.znf143[which(annotdata.znf143$y=="Yes"),2], alternative = "two.sided")

perm.pval <- pvalue(oneway_test(annotdata.znf143[,2] ~ annotdata.znf143[,1],
                     data=annotdata.znf143,
                     alternative="greater", 
                     distribution=approximate(B=10000)))[1]

perm.pval <- ifelse(perm.pval==0,"< 0.0001", as.character(round(perm.pval,4)))

plottitle <- paste(gsub(paste(c("Gm12878",
                                  "-","_",
                                  "dist","perc","count",
                                  "Haib",
                                  "Sydh",
                                  "Uta",
                                  "Uw",
                                  "Broad",
                                  "Uchicago"), 
                                collapse = "|"), 
                          "",
                          "Gm12878-Znf143166181ap-Sydh_dist"))

p.gm12878.10kb.znf143 <- ggplot(annotdata.znf143, aes(x=Znf143166181ap_dist, color=y)) +
    geom_density() +
    scale_color_discrete(name="Class of\nGenomic Bin",
                         labels=c("Does not overlap\nw/ flanked TAD boundary", "Overlapped w/\nflanked TAD boundary")) +
    ylab("") +
    xlab("") +
    ggtitle("ZNF143\nPermutation P-Value: < 0.0001") +
    #annotate("text", x=7, y=.2, label= paste("P-Value:", perm.pval, sep = " "), size=5) +
    theme_bw() +
    theme(axis.text.x = element_text(size=15 #,
                                     #angle = 45, 
                                     #margin = ggplot2::margin(t = 35),
                                     #hjust = 1
    ),
    axis.text.y = element_text(size = 15),
    axis.title.x = element_text(size = 20),
    axis.title.y = element_text(size = 20),
    legend.text=element_text(size=15),
    legend.title=element_text(size=20),
    plot.title = element_text(size=20,
                              hjust=.5))
```

####CTCF

```{r}
annotname <- gsub(paste(c("`", 
             "Gm12878", 
             "-", 
             #"_", 
             #"dist", "count", "perc",
             "Haib", 
             "Sydh",
             "Uta",
             "Uw",
             "Broad",
             "Uchicago"), collapse = "|"), "", "Gm12878-Ctcf-Broad_dist")

annotdata.ctcf <- train_smote[, c(1, which(names(train_smote)==annotname))]

#ks.test(annotdata.ctcf[which(annotdata.ctcf$y=="No"),2], annotdata.ctcf[which(annotdata.ctcf$y=="Yes"),2], alternative = "two.sided")

perm.pval <- pvalue(oneway_test(annotdata.ctcf[,2] ~ annotdata.ctcf[,1],
                     data=annotdata.ctcf,
                     alternative="greater", 
                     distribution=approximate(B=10000)))[1]

perm.pval <- ifelse(perm.pval==0,"< 0.0001", as.character(round(perm.pval,4)))

plottitle <- paste(gsub(paste(c("Gm12878",
                                  "-","_",
                                  "dist","perc","count",
                                  "Haib",
                                  "Sydh",
                                  "Uta",
                                  "Uw",
                                  "Broad",
                                  "Uchicago"), 
                                collapse = "|"), 
                          "",
                          "Gm12878-Ctcf-Broad_dist"))

p.gm12878.10kb.ctcf <- ggplot(annotdata.ctcf, aes(x=Ctcf_dist, color=y)) +
    geom_density() +
    scale_color_discrete(name="Class of\nGenomic Bin",
                         labels=c("Does not overlap\nw/ flanked TAD boundary", "Overlapped w/\nflanked TAD boundary")) +
    ylab("") +
    xlab("") +
    ggtitle("CTCF\nPermutation P-Value: < 0.0001") +
    #annotate("text", x=7, y=.2, label= paste("P-Value:", perm.pval, sep = " "), size=5) +
    theme_bw() +
    theme(axis.text.x = element_text(size=15 #,
                                     #angle = 45, 
                                     #margin = ggplot2::margin(t = 35),
                                     #hjust = 1
    ),
    axis.text.y = element_text(size = 15),
    axis.title.x = element_text(size = 20),
    axis.title.y = element_text(size = 20),
    legend.text=element_text(size=15),
    legend.title=element_text(size=20),
    plot.title = element_text(size=20,
                              hjust=.5))
```

####RAD21

```{r}
annotname <- gsub(paste(c("`", 
             "Gm12878", 
             "-", 
             #"_", 
             #"dist", "count", "perc",
             "Haib", 
             "Sydh",
             "Uta",
             "Uw",
             "Broad",
             "Uchicago"), collapse = "|"), "", "Gm12878-Rad21-Haib_dist")

annotdata.rad21 <- train_smote[, c(1, which(names(train_smote)==annotname))]

#ks.test(annotdata.rad21[which(annotdata.rad21$y=="No"),2], annotdata.rad21[which(annotdata.rad21$y=="Yes"),2], alternative = "two.sided")

perm.pval <- pvalue(oneway_test(annotdata.rad21[,2] ~ annotdata.rad21[,1],
                     data=annotdata.rad21,
                     alternative="greater", 
                     distribution=approximate(B=10000)))[1]

perm.pval <- ifelse(perm.pval==0,"< 0.0001", as.character(round(perm.pval,4)))

plottitle <- paste(gsub(paste(c("Gm12878",
                                  "-","_",
                                  "dist","perc","count",
                                  "Haib",
                                  "Sydh",
                                  "Uta",
                                  "Uw",
                                  "Broad",
                                  "Uchicago"), 
                                collapse = "|"), 
                          "",
                          "Gm12878-Rad21-Haib_dist"))

p.gm12878.10kb.rad21 <- ggplot(annotdata.rad21, aes(x=Rad21_dist, color=y)) +
    geom_density() +
    scale_color_discrete(name="Class of\nGenomic Bin",
                         labels=c("Does not overlap\nw/ flanked TAD boundary", "Overlapped w/\nflanked TAD boundary")) +
    ylab("") +
    xlab("") +
    ggtitle("RAD21\nPermutation P-Value: < 0.0001") +
    #annotate("text", x=7, y=.2, label= paste("P-Value:", perm.pval, sep = " "), size=5) +
    theme_bw() +
    theme(axis.text.x = element_text(size=15 #,
                                     #angle = 45, 
                                     #margin = ggplot2::margin(t = 35),
                                     #hjust = 1
    ),
    axis.text.y = element_text(size = 15),
    axis.title.x = element_text(size = 20),
    axis.title.y = element_text(size = 20),
    legend.text=element_text(size=15),
    legend.title=element_text(size=20),
    plot.title = element_text(size=20,
                              hjust=.5))
```

## 25kb

```{r}
train <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/25kb/training_testing/train.rds"))

enetcoefs <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/Distance/ENET/enetcoefs.rds"))

names(train) <- gsub(paste(c("`", 
                             "Gm12878", 
                             "-", 
                             #"_", 
                             #"dist", "count", "perc",
                             "Haib", 
                             "Sydh",
                             "Uta",
                             "Uw",
                             "Broad",
                             "Uchicago"), collapse = "|"), "", names(train))
train <- train[,c(1,which(names(train) %in% enetcoefs))]

set.seed(123)
train_smote <- SMOTE(y ~ ., 
                     data=train, 
                     perc.over = 100, 
                     perc.under = 200)

### Top Annotations

####SMC

```{r}
annotname <- gsub(paste(c("`", 
             "Gm12878", 
             "-", 
             #"_", 
             #"dist", "count", "perc",
             "Haib", 
             "Sydh",
             "Uta",
             "Uw",
             "Broad",
             "Uchicago"), collapse = "|"), "", "Gm12878-Smc3ab9263-Sydh_dist")

annotdata.smc <- train_smote[, c(1, which(names(train_smote)==annotname))]

#ks.test(annotdata.smc[which(annotdata.smc$y=="No"),2], annotdata.smc[which(annotdata.smc$y=="Yes"),2], alternative = "two.sided")

perm.pval <- pvalue(oneway_test(annotdata.smc[,2] ~ annotdata.smc[,1],
                     data=annotdata.smc,
                     alternative="greater", 
                     distribution=approximate(B=10000)))[1]

perm.pval <- ifelse(perm.pval==0,"< 0.0001", as.character(round(perm.pval,4)))

plottitle <- paste(gsub(paste(c("Gm12878",
                                  "-","_",
                                  "dist","perc","count",
                                  "Haib",
                                  "Sydh",
                                  "Uta",
                                  "Uw",
                                  "Broad",
                                  "Uchicago"), 
                                collapse = "|"), 
                          "",
                          "Gm12878-Smc3ab9263-Sydh_dist"))

p.gm12878.25kb.smc <- ggplot(annotdata.smc, aes(x=Smc3ab9263_dist, color=y)) +
    geom_density() +
    scale_color_discrete(name="Class of\nGenomic Bin",
                         labels=c("Does not overlap\nw/ flanked TAD boundary", "Overlapped w/\nflanked TAD boundary")) +
    ylab("") +
    xlab("") +
    ggtitle("SMC3a\nPermutation P-Value: < 0.0001") +
    #annotate("text", x=7, y=.2, label= paste("P-Value:", perm.pval, sep = " "), size=5) +
    theme_bw() +
    theme(axis.text.x = element_text(size=15 #,
                                     #angle = 45, 
                                     #margin = ggplot2::margin(t = 35),
                                     #hjust = 1
    ),
    axis.text.y = element_text(size = 15),
    axis.title.x = element_text(size = 20),
    axis.title.y = element_text(size = 20),
    legend.text=element_text(size=15),
    legend.title=element_text(size=20),
    plot.title = element_text(size=20,
                              hjust=.5))
```

####ZNF143

```{r}
annotname <- gsub(paste(c("`", 
             "Gm12878", 
             "-", 
             #"_", 
             #"dist", "count", "perc",
             "Haib", 
             "Sydh",
             "Uta",
             "Uw",
             "Broad",
             "Uchicago"), collapse = "|"), "", "Gm12878-Znf143166181ap-Sydh_dist")

annotdata.znf143 <- train_smote[, c(1, which(names(train_smote)==annotname))]

#ks.test(annotdata.znf143[which(annotdata.znf143$y=="No"),2], annotdata.znf143[which(annotdata.znf143$y=="Yes"),2], alternative = "two.sided")

perm.pval <- pvalue(oneway_test(annotdata.znf143[,2] ~ annotdata.znf143[,1],
                     data=annotdata.znf143,
                     alternative="greater", 
                     distribution=approximate(B=10000)))[1]

perm.pval <- ifelse(perm.pval==0,"< 0.0001", as.character(round(perm.pval,4)))

plottitle <- paste(gsub(paste(c("Gm12878",
                                  "-","_",
                                  "dist","perc","count",
                                  "Haib",
                                  "Sydh",
                                  "Uta",
                                  "Uw",
                                  "Broad",
                                  "Uchicago"), 
                                collapse = "|"), 
                          "",
                          "Gm12878-Znf143166181ap-Sydh_dist"))

p.gm12878.25kb.znf143 <- ggplot(annotdata.znf143, aes(x=Znf143166181ap_dist, color=y)) +
    geom_density() +
    scale_color_discrete(name="Class of\nGenomic Bin",
                         labels=c("Does not overlap\nw/ flanked TAD boundary", "Overlapped w/\nflanked TAD boundary")) +
    ylab("") +
    xlab("") +
    ggtitle("ZNF143\nPermutation P-Value: < 0.0001") +
    #annotate("text", x=7, y=.2, label= paste("P-Value:", perm.pval, sep = " "), size=5) +
    theme_bw() +
    theme(axis.text.x = element_text(size=15 #,
                                     #angle = 45, 
                                     #margin = ggplot2::margin(t = 35),
                                     #hjust = 1
    ),
    axis.text.y = element_text(size = 15),
    axis.title.x = element_text(size = 20),
    axis.title.y = element_text(size = 20),
    legend.text=element_text(size=15),
    legend.title=element_text(size=20),
    plot.title = element_text(size=20,
                              hjust=.5))
```

####CTCF

```{r}
annotname <- gsub(paste(c("`", 
             "Gm12878", 
             "-", 
             #"_", 
             #"dist", "count", "perc",
             "Haib", 
             "Sydh",
             "Uta",
             "Uw",
             "Broad",
             "Uchicago"), collapse = "|"), "", "Gm12878-Ctcf-Broad_dist")

annotdata.ctcf <- train_smote[, c(1, which(names(train_smote)==annotname))]

#ks.test(annotdata.ctcf[which(annotdata.ctcf$y=="No"),2], annotdata.ctcf[which(annotdata.ctcf$y=="Yes"),2], alternative = "two.sided")

perm.pval <- pvalue(oneway_test(annotdata.ctcf[,2] ~ annotdata.ctcf[,1],
                     data=annotdata.ctcf,
                     alternative="greater", 
                     distribution=approximate(B=10000)))[1]

perm.pval <- ifelse(perm.pval==0,"< 0.0001", as.character(round(perm.pval,4)))

plottitle <- paste(gsub(paste(c("Gm12878",
                                  "-","_",
                                  "dist","perc","count",
                                  "Haib",
                                  "Sydh",
                                  "Uta",
                                  "Uw",
                                  "Broad",
                                  "Uchicago"), 
                                collapse = "|"), 
                          "",
                          "Gm12878-Ctcf-Broad_dist"))

p.gm12878.25kb.ctcf <- ggplot(annotdata.ctcf, aes(x=Ctcf_dist, color=y)) +
    geom_density() +
    scale_color_discrete(name="Class of\nGenomic Bin",
                         labels=c("Does not overlap\nw/ flanked TAD boundary", "Overlapped w/\nflanked TAD boundary")) +
    ylab("") +
    xlab("") +
    ggtitle("CTCF\nPermutation P-Value: < 0.0001") +
    #annotate("text", x=7, y=.2, label= paste("P-Value:", perm.pval, sep = " "), size=5) +
    theme_bw() +
    theme(axis.text.x = element_text(size=15 #,
                                     #angle = 45, 
                                     #margin = ggplot2::margin(t = 35),
                                     #hjust = 1
    ),
    axis.text.y = element_text(size = 15),
    axis.title.x = element_text(size = 20),
    axis.title.y = element_text(size = 20),
    legend.text=element_text(size=15),
    legend.title=element_text(size=20),
    plot.title = element_text(size=20,
                              hjust=.5))
```

####RAD21

```{r}
annotname <- gsub(paste(c("`", 
             "Gm12878", 
             "-", 
             #"_", 
             #"dist", "count", "perc",
             "Haib", 
             "Sydh",
             "Uta",
             "Uw",
             "Broad",
             "Uchicago"), collapse = "|"), "", "Gm12878-Rad21-Haib_dist")

annotdata.rad21 <- train_smote[, c(1, which(names(train_smote)==annotname))]

#ks.test(annotdata.rad21[which(annotdata.rad21$y=="No"),2], annotdata.rad21[which(annotdata.rad21$y=="Yes"),2], alternative = "two.sided")

perm.pval <- pvalue(oneway_test(annotdata.rad21[,2] ~ annotdata.rad21[,1],
                     data=annotdata.rad21,
                     alternative="greater", 
                     distribution=approximate(B=10000)))[1]

perm.pval <- ifelse(perm.pval==0,"< 0.0001", as.character(round(perm.pval,4)))

plottitle <- paste(gsub(paste(c("Gm12878",
                                  "-","_",
                                  "dist","perc","count",
                                  "Haib",
                                  "Sydh",
                                  "Uta",
                                  "Uw",
                                  "Broad",
                                  "Uchicago"), 
                                collapse = "|"), 
                          "",
                          "Gm12878-Rad21-Haib_dist"))

p.gm12878.25kb.rad21 <- ggplot(annotdata.rad21, aes(x=Rad21_dist, color=y)) +
    geom_density() +
    scale_color_discrete(name="Class of\nGenomic Bin",
                         labels=c("Does not overlap\nw/ flanked TAD boundary", "Overlapped w/\nflanked TAD boundary")) +
    ylab("") +
    xlab("") +
    ggtitle("RAD21\nPermutation P-Value: < 0.0001") +
    #annotate("text", x=7, y=.2, label= paste("P-Value:", perm.pval, sep = " "), size=5) +
    theme_bw() +
    theme(axis.text.x = element_text(size=15 #,
                                     #angle = 45, 
                                     #margin = ggplot2::margin(t = 35),
                                     #hjust = 1
    ),
    axis.text.y = element_text(size = 15),
    axis.title.x = element_text(size = 20),
    axis.title.y = element_text(size = 20),
    legend.text=element_text(size=15),
    legend.title=element_text(size=20),
    plot.title = element_text(size=20,
                              hjust=.5))
```

## 50kb

```{r}
train <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/50kb/training_testing/train.rds"))

enetcoefs <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/Distance/ENET/enetcoefs.rds"))

names(train) <- gsub(paste(c("`", 
                             "Gm12878", 
                             "-", 
                             #"_", 
                             #"dist", "count", "perc",
                             "Haib", 
                             "Sydh",
                             "Uta",
                             "Uw",
                             "Broad",
                             "Uchicago"), collapse = "|"), "", names(train))
train <- train[,c(1,which(names(train) %in% enetcoefs))]

set.seed(123)
train_smote <- SMOTE(y ~ ., 
                     data=train, 
                     perc.over = 100, 
                     perc.under = 200)

### Top Annotations

####SMC

```{r}
annotname <- gsub(paste(c("`", 
             "Gm12878", 
             "-", 
             #"_", 
             #"dist", "count", "perc",
             "Haib", 
             "Sydh",
             "Uta",
             "Uw",
             "Broad",
             "Uchicago"), collapse = "|"), "", "Gm12878-Smc3ab9263-Sydh_dist")

annotdata.smc <- train_smote[, c(1, which(names(train_smote)==annotname))]

#ks.test(annotdata.smc[which(annotdata.smc$y=="No"),2], annotdata.smc[which(annotdata.smc$y=="Yes"),2], alternative = "two.sided")

perm.pval <- pvalue(oneway_test(annotdata.smc[,2] ~ annotdata.smc[,1],
                     data=annotdata.smc,
                     alternative="greater", 
                     distribution=approximate(B=10000)))[1]

perm.pval <- ifelse(perm.pval==0,"< 0.0001", as.character(round(perm.pval,4)))

plottitle <- paste(gsub(paste(c("Gm12878",
                                  "-","_",
                                  "dist","perc","count",
                                  "Haib",
                                  "Sydh",
                                  "Uta",
                                  "Uw",
                                  "Broad",
                                  "Uchicago"), 
                                collapse = "|"), 
                          "",
                          "Gm12878-Smc3ab9263-Sydh_dist"))

p.gm12878.50kb.smc <- ggplot(annotdata.smc, aes(x=Smc3ab9263_dist, color=y)) +
    geom_density() +
    scale_color_discrete(name="Class of\nGenomic Bin",
                         labels=c("Does not overlap\nw/ flanked TAD boundary", "Overlapped w/\nflanked TAD boundary")) +
    ylab("") +
    xlab("") +
    ggtitle("SMC3a\nPermutation P-Value: < 0.0001") +
    #annotate("text", x=7, y=.2, label= paste("P-Value:", perm.pval, sep = " "), size=5) +
    theme_bw() +
    theme(axis.text.x = element_text(size=15 #,
                                     #angle = 45, 
                                     #margin = ggplot2::margin(t = 35),
                                     #hjust = 1
    ),
    axis.text.y = element_text(size = 15),
    axis.title.x = element_text(size = 20),
    axis.title.y = element_text(size = 20),
    legend.text=element_text(size=15),
    legend.title=element_text(size=20),
    plot.title = element_text(size=20,
                              hjust=.5))
```

####ZNF143

```{r}
annotname <- gsub(paste(c("`", 
             "Gm12878", 
             "-", 
             #"_", 
             #"dist", "count", "perc",
             "Haib", 
             "Sydh",
             "Uta",
             "Uw",
             "Broad",
             "Uchicago"), collapse = "|"), "", "Gm12878-Znf143166181ap-Sydh_dist")

annotdata.znf143 <- train_smote[, c(1, which(names(train_smote)==annotname))]

#ks.test(annotdata.znf143[which(annotdata.znf143$y=="No"),2], annotdata.znf143[which(annotdata.znf143$y=="Yes"),2], alternative = "two.sided")

perm.pval <- pvalue(oneway_test(annotdata.znf143[,2] ~ annotdata.znf143[,1],
                     data=annotdata.znf143,
                     alternative="greater", 
                     distribution=approximate(B=10000)))[1]

perm.pval <- ifelse(perm.pval==0,"< 0.0001", as.character(round(perm.pval,4)))

plottitle <- paste(gsub(paste(c("Gm12878",
                                  "-","_",
                                  "dist","perc","count",
                                  "Haib",
                                  "Sydh",
                                  "Uta",
                                  "Uw",
                                  "Broad",
                                  "Uchicago"), 
                                collapse = "|"), 
                          "",
                          "Gm12878-Znf143166181ap-Sydh_dist"))

p.gm12878.50kb.znf143 <- ggplot(annotdata.znf143, aes(x=Znf143166181ap_dist, color=y)) +
    geom_density() +
    scale_color_discrete(name="Class of\nGenomic Bin",
                         labels=c("Does not overlap\nw/ flanked TAD boundary", "Overlapped w/\nflanked TAD boundary")) +
    ylab("") +
    xlab("") +
    ggtitle("ZNF143\nPermutation P-Value: < 0.0001") +
    #annotate("text", x=7, y=.2, label= paste("P-Value:", perm.pval, sep = " "), size=5) +
    theme_bw() +
    theme(axis.text.x = element_text(size=15 #,
                                     #angle = 45, 
                                     #margin = ggplot2::margin(t = 35),
                                     #hjust = 1
    ),
    axis.text.y = element_text(size = 15),
    axis.title.x = element_text(size = 20),
    axis.title.y = element_text(size = 20),
    legend.text=element_text(size=15),
    legend.title=element_text(size=20),
    plot.title = element_text(size=20,
                              hjust=.5))
```

####CTCF

```{r}
annotname <- gsub(paste(c("`", 
             "Gm12878", 
             "-", 
             #"_", 
             #"dist", "count", "perc",
             "Haib", 
             "Sydh",
             "Uta",
             "Uw",
             "Broad",
             "Uchicago"), collapse = "|"), "", "Gm12878-Ctcf-Broad_dist")

annotdata.ctcf <- train_smote[, c(1, which(names(train_smote)==annotname))]

#ks.test(annotdata.ctcf[which(annotdata.ctcf$y=="No"),2], annotdata.ctcf[which(annotdata.ctcf$y=="Yes"),2], alternative = "two.sided")

perm.pval <- pvalue(oneway_test(annotdata.ctcf[,2] ~ annotdata.ctcf[,1],
                     data=annotdata.ctcf,
                     alternative="greater", 
                     distribution=approximate(B=10000)))[1]

perm.pval <- ifelse(perm.pval==0,"< 0.0001", as.character(round(perm.pval,4)))

plottitle <- paste(gsub(paste(c("Gm12878",
                                  "-","_",
                                  "dist","perc","count",
                                  "Haib",
                                  "Sydh",
                                  "Uta",
                                  "Uw",
                                  "Broad",
                                  "Uchicago"), 
                                collapse = "|"), 
                          "",
                          "Gm12878-Ctcf-Broad_dist"))

p.gm12878.50kb.ctcf <- ggplot(annotdata.ctcf, aes(x=Ctcf_dist, color=y)) +
    geom_density() +
    scale_color_discrete(name="Class of\nGenomic Bin",
                         labels=c("Does not overlap\nw/ flanked TAD boundary", "Overlapped w/\nflanked TAD boundary")) +
    ylab("") +
    xlab("") +
    ggtitle("CTCF\nPermutation P-Value: < 0.0001") +
    #annotate("text", x=7, y=.2, label= paste("P-Value:", perm.pval, sep = " "), size=5) +
    theme_bw() +
    theme(axis.text.x = element_text(size=15 #,
                                     #angle = 45, 
                                     #margin = ggplot2::margin(t = 35),
                                     #hjust = 1
    ),
    axis.text.y = element_text(size = 15),
    axis.title.x = element_text(size = 20),
    axis.title.y = element_text(size = 20),
    legend.text=element_text(size=15),
    legend.title=element_text(size=20),
    plot.title = element_text(size=20,
                              hjust=.5))
```

####RAD21

```{r}
annotname <- gsub(paste(c("`", 
             "Gm12878", 
             "-", 
             #"_", 
             #"dist", "count", "perc",
             "Haib", 
             "Sydh",
             "Uta",
             "Uw",
             "Broad",
             "Uchicago"), collapse = "|"), "", "Gm12878-Rad21-Haib_dist")

annotdata.rad21 <- train_smote[, c(1, which(names(train_smote)==annotname))]

#ks.test(annotdata.rad21[which(annotdata.rad21$y=="No"),2], annotdata.rad21[which(annotdata.rad21$y=="Yes"),2], alternative = "two.sided")

perm.pval <- pvalue(oneway_test(annotdata.rad21[,2] ~ annotdata.rad21[,1],
                     data=annotdata.rad21,
                     alternative="greater", 
                     distribution=approximate(B=10000)))[1]

perm.pval <- ifelse(perm.pval==0,"< 0.0001", as.character(round(perm.pval,4)))

plottitle <- paste(gsub(paste(c("Gm12878",
                                  "-","_",
                                  "dist","perc","count",
                                  "Haib",
                                  "Sydh",
                                  "Uta",
                                  "Uw",
                                  "Broad",
                                  "Uchicago"), 
                                collapse = "|"), 
                          "",
                          "Gm12878-Rad21-Haib_dist"))
